\documentclass{article}
\usepackage{amssymb}
\usepackage{graphicx} % Required for inserting images

\begin{document}

\section{Survey Questions}\label{survey}
This appendix includes the full survey presented to respondents. Some questions are only presented to respondents depending on answers to preceding questions, meaning not all questions are seen by every respondent. Answer choices that were added during pre-processing are shown in italics.

\newcommand{\checkbox}{$\square$\ }
 
% Reduce spacing in item lists
 
\begin{enumerate}
 

\item \textbf{Introduction}

Researchers at the National Renewable Energy Laboratory and Colorado School of Mines are working to understand residential electricity customers' willingness to participate in demand flexibility programs offered by their electric utility. Demand flexibility refers to the action of changing electricity usage by shifting or reducing consumption in response to incentives offered or requests made by their electric utility.
 
The goal of this survey is to understand the associations between residential customers' backgrounds and their willingness to be flexible in their electricity consumption. By better understanding electric demand flexibility, electric utilities can introduce flexibility programs that can lead to cost savings (for both the utility and customers) and improve the overall reliability and security of the power grid.
 
This survey should take between 15 and 20 minutes to complete and asks questions regarding your electric utility, billing, housing, and electricity usage behavior.
 

\item Do you live in Colorado or Tennessee?
\begin{itemize}
  \item[\checkbox] Colorado
  \item[\checkbox] Tennessee
  \item[\checkbox] Neither
\end{itemize}
 

\item What is your zip code?\\
Free response
 

\item What is your age?
\begin{itemize}
  \item[\checkbox] 18--24 years
  \item[\checkbox] 25--34 years
  \item[\checkbox] 35--44 years
  \item[\checkbox] 45--54 years
  \item[\checkbox] 55--59 years
  \item[\checkbox] 60--64 years
  \item[\checkbox] 65 years and over
\end{itemize}
 

\item What is your ethnicity?
\begin{itemize}
  \item[\checkbox] American Indian or Alaska Native
  \item[\checkbox] Asian or Asian American
  \item[\checkbox] Black or African American
  \item[\checkbox] Hispanic or Latino
  \item[\checkbox] Native Hawaiian or Pacific Islander
  \item[\checkbox] White or Caucasian
  \item[\checkbox] Biracial or Multiracial
  \item[\checkbox] Other (key in)
  \item[\checkbox] Prefer not to say
\end{itemize}
 

\item What is the primary language spoken in your home?
\begin{itemize}
  \item[\checkbox] English
  \item[\checkbox] Spanish
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Are there any adults in your household who do not speak English?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item What is your education level?
\begin{itemize}
  \item[\checkbox] Elementary school
  \item[\checkbox] Middle school
  \item[\checkbox] High school
  \item[\checkbox] \textit{Some high school, no degree}
  \item[\checkbox] Some college, no degree
  \item[\checkbox] Associate's degree
  \item[\checkbox] Bachelor's degree
  \item[\checkbox] Master's degree
  \item[\checkbox] Doctorate
  \item[\checkbox] Vocational school
  \item[\checkbox] Professional training
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item What is your employment status?
\begin{itemize}
  \item[\checkbox] Employed full-time
  \item[\checkbox] Employed part-time
  \item[\checkbox] Self employed
  \item[\checkbox] Homemaker
  \item[\checkbox] Full-time student
  \item[\checkbox] Retired
  \item[\checkbox] Disabled, unable to work
  \item[\checkbox] Unemployed
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested from above (Tennessee residents):} What is your household income?
(median household income in Tennessee per the 2023 ACS: \$67,000 [S1901])
\begin{itemize}
  \item[\checkbox] \$29,999 or lower
  \item[\checkbox] \$30,000 to \$64,999
  \item[\checkbox] \$65,000 to \$89,999
  \item[\checkbox] \$90,000 to \$119,999
  \item[\checkbox] \$120,000 to \$149,999
  \item[\checkbox] \$150,000 or higher
  \item[\checkbox] Prefer not to say
\end{itemize}
 

\item \textit{Nested from above (Colorado residents or ``Neither''):} What is your household income?
(median household income in Colorado per the 2023 ACS: \$92,000 [S1901])
\begin{itemize}
  \item[\checkbox] \$29,999 or lower
  \item[\checkbox] \$30,000 to \$59,999
  \item[\checkbox] \$60,000 to \$89,999
  \item[\checkbox] \$90,000 to \$119,999
  \item[\checkbox] \$120,000 to \$149,999
  \item[\checkbox] \$150,000 or higher
  \item[\checkbox] Prefer not to say
\end{itemize}
 

\item How many people (including you) live in your household?
\begin{itemize}
  \item[\checkbox] 1
  \item[\checkbox] 2--3
  \item[\checkbox] 4--5
  \item[\checkbox] 6 or more
\end{itemize}
 

\item How many people over the age of 65 (including you) live in your household?
\begin{itemize}
  \item[\checkbox] None
  \item[\checkbox] 1
  \item[\checkbox] 2
  \item[\checkbox] 3 or more
\end{itemize}
 

\item How many children under the age of 5 live in your household?
\begin{itemize}
  \item[\checkbox] None
  \item[\checkbox] 1
  \item[\checkbox] 2--3
  \item[\checkbox] 4--5
  \item[\checkbox] 6 or more
\end{itemize}
 

\item How often do you struggle to afford essentials (e.g., food, medications, energy, etc.)?
\begin{itemize}
  \item[\checkbox] Never
  \item[\checkbox] Rarely (once in a while)
  \item[\checkbox] Occasionally (a few times a month)
  \item[\checkbox] Frequently (several times a month)
  \item[\checkbox] Regularly (weekly)
  \item[\checkbox] Always
\end{itemize}
 

\item \textit{Nested from above (Colorado residents} Who is your electricity provider?
\begin{itemize}
  \item[\checkbox] Colorado Springs Utilities (C)
  \item[\checkbox] CORE Electric (C)
  \item[\checkbox] Delta-Montrose Electric Association (C)
  \item[\checkbox] Empire Electric Association Inc.\ (C)
  \item[\checkbox] Grand Valley Rural Power Lines Inc.\ (C)
  \item[\checkbox] Gunnison Canyon Electric Association Inc.\ (C)
  \item[\checkbox] Highline Electric Association (C)
  \item[\checkbox] Holy Cross Energy (C)
  \item[\checkbox] K.C.\ Electric Association (C)
  \item[\checkbox] La Plata Electric Association Inc.\ (C)
  \item[\checkbox] Morgan County Rural Electric Association (C)
  \item[\checkbox] Mountain Parks Electric Inc.\ (C)
  \item[\checkbox] Mountain View (C)
  \item[\checkbox] Poudre Valley Rural Electric Association Inc.\ (C)
  \item[\checkbox] San Isabel Electric Association Inc.\ (C)
  \item[\checkbox] San Luis Valley Rural Electric Cooperative Inc.\ (C)
  \item[\checkbox] San Miguel Power Association Inc.\ (C)
  \item[\checkbox] Sangre De Cristo Electric Association Inc.\ (C)
  \item[\checkbox] Southeast Colorado Power Association (C)
  \item[\checkbox] United Power Inc.\ (C)
  \item[\checkbox] White River Electric Association (C)
  \item[\checkbox] Y-W Electric Association Inc.\ (C)
  \item[\checkbox] Yampa Valley Electric Association Inc.\ (C)
  \item[\checkbox] Xcel (C)
  \item[\checkbox] Other (key in)
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested from above (Tennessee residents):} Who is your electricity provider?
\begin{itemize}
  \item[\checkbox] Appalachian Electric Cooperative
  \item[\checkbox] Blue Ridge Mountain Electric Membership Corporation
  \item[\checkbox] Caney Fork Electric Cooperative
  \item[\checkbox] Chickasaw Electric Coop
  \item[\checkbox] Cumberland Electric Membership Corp
  \item[\checkbox] Duck River Electric Membership Corp
  \item[\checkbox] EPB
  \item[\checkbox] Fayettville Public Util
  \item[\checkbox] Forked Deer Electric Coop Inc
  \item[\checkbox] Fort Loudoun Electric Coop
  \item[\checkbox] Gibson Electric Membership Corp
  \item[\checkbox] HolstonElectric Coop inc
  \item[\checkbox] Middle Tennessee Electric Membership Corporation
  \item[\checkbox] Meriwether Lewis Electric Membership Corp
  \item[\checkbox] Mountain Electric Coop Inc
  \item[\checkbox] North Georgia Electric Membership Corp
  \item[\checkbox] Pickwick Electric Corp
  \item[\checkbox] Plateau Electric Coop
  \item[\checkbox] Powell Valley Electric Coop
  \item[\checkbox] Sequachee Valley Electric Coop
  \item[\checkbox] Southwest Tennessee Electric Membership Corp
  \item[\checkbox] Tennessee Valley Electric Coop
  \item[\checkbox] Tri-County Electric Membership Corp
  \item[\checkbox] Tri-State Electric Membership Corp
  \item[\checkbox] Upper Cumberland Electric Membership Corp
  \item[\checkbox] Volunteer Energy Coop
  \item[\checkbox] I don't know
  \item[\checkbox] Other
\end{itemize}
 

\item Do you know which electricity rate you are enrolled in?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] My utility costs are included in my rent
\end{itemize}
 

\item \textit{Nested from above (If they indicate which electricity rate they are enrolled in):}
Select the rate type you are enrolled in.
\begin{itemize}
  \item[\checkbox] Flat rate (electricity costs the same at all times of the day and/or year)
  \item[\checkbox] Tiered rate (electricity price increases as the amount of energy consumed per billing period increases)
  \item[\checkbox] TOU/time-varying rate (the price of electricity depends on the time of day and/or year)
  \item[\checkbox] Appliance-specific rate (the utility offers a rebate or reduced rate based on direct control of an appliance e.g.\ A/C)
  \item[\checkbox] EV-specific rate (the price of electricity is dependent on the ownership of an electric vehicle)
  \item[\checkbox] Transactional rate (the price of electricity is dependent on the wholesale electricity market)
  \item[\checkbox] \textit{Solar energy rate or net energy metering rate}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested from above (if they indicate they have an appliance-specific rate):}
Which appliance does your electricity rate apply to?
\begin{itemize}
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Heating
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested from above (If they indicate the electricity rate in which they are enrolled):}
Did you choose to be enrolled in this rate?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] I don't know/don't remember
\end{itemize}
 

\item \textit{Nested from above (If they indicate which electricity rate they are enrolled in):}
Who do you think benefits the most through this electricity rate?
\begin{itemize}
  \item[\checkbox] Both me and the electric utility
  \item[\checkbox] Only the electric utility
  \item[\checkbox] Only me
  \item[\checkbox] Society
  \item[\checkbox] Nobody. These rates have no impacts
\end{itemize}
 

\item Have you ever received a notification from the electric utility or any other entity regarding an emergency need for reducing demand (for example, to avoid rolling blackouts during a heatwave, the utility may have asked you to reduce your A/C usage)?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] I don't know/don't remember
\end{itemize}
 

\item \textit{Nested from above (If they indicate they have received an alert from someone):}
Do you comply with these requests?
\begin{itemize}
  \item[\checkbox] Always
  \item[\checkbox] Yes, if it does not create major inconvenience
  \item[\checkbox] Yes, if it does not create any inconvenience
  \item[\checkbox] Never
  \item[\checkbox] I do not have an option to decline, i.e., is mandatory
\end{itemize}
 

\item \textit{Nested from above (If they indicate they have received an alert):}
Who in your home usually responds to a request from the electric utility to change your electricity usage?
\begin{itemize}
  \item[\checkbox] Only an adult
  \item[\checkbox] Anyone in the household
  \item[\checkbox] It is not possible to decline the request, i.e.\ is mandatory
\end{itemize}
 

\item \textit{Nested from above (If they indicate they have received an alert from someone):}
How did you receive this information?
\begin{itemize}
  \item[\checkbox] Text message
  \item[\checkbox] Telephone call
  \item[\checkbox] Email
  \item[\checkbox] News (television, radio, etc.)
  \item[\checkbox] \textit{Physical marketing materials (mail, on the bill, door note)}
  \item[\checkbox] \textit{Social media}
  \item[\checkbox] \textit{I don't know}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Are you in charge of making the payment for the electricity bill each period (manually or automatically)?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] My utility costs are included in my rent
\end{itemize}
 

\item \textit{Nested from above (If they indicate they are the one who pays the bill):}
How is this payment processed each billing period?
\begin{itemize}
  \item[\checkbox] Pay manually online
  \item[\checkbox] Pay manually by mail
  \item[\checkbox] Autopay
\end{itemize}
 

\item Do you review your electricity bill?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they indicate they review their bill):}
How frequently do you review the billing statement received from your electricity provider?
\begin{itemize}
  \item[\checkbox] Every billing period
  \item[\checkbox] Once every few months
  \item[\checkbox] Once a year
  \item[\checkbox] Only when the bill seems exceptionally high
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested from above (if they indicate they review their bill):}
What sections of the bill do you review? (Select all that apply)
\begin{itemize}
  \item[\checkbox] The total charge
  \item[\checkbox] How many kWh were consumed over the billing period
  \item[\checkbox] The kWh related to each tier charge
  \item[\checkbox] Every charge item on the bill
  \item[\checkbox] \textit{Comparison to previous bills}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item What best describes your residence?
\begin{itemize}
  \item[\checkbox] Single family house (no shared walls with other homes)
  \item[\checkbox] Townhouse
  \item[\checkbox] Condominium
  \item[\checkbox] Duplex or triplex
  \item[\checkbox] Multi-family apartment building
  \item[\checkbox] Manufactured or mobile home
  \item[\checkbox] \textit{Assisted living}
  \item[\checkbox] \textit{Vehicle (camper, trailer, or car}
  \item[\checkbox] \textit{Homeless}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Do you own or rent your residence?
\begin{itemize}
  \item[\checkbox] Own
  \item[\checkbox] Rent
  \item[\checkbox] Neither, for instance living with family
\end{itemize}
 

\item To the best of your knowledge, when was your home built?
\begin{itemize}
  \item[\checkbox] Pre 1900
  \item[\checkbox] 1900--1950
  \item[\checkbox] 1950--1970
  \item[\checkbox] 1970--2015
  \item[\checkbox] I don't know
\end{itemize}
 

\item Have there been any major renovations to the home that you are aware of?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested from above (If they indicate that there have been any renovations in their home):}
What types of renovations are you aware of?
\begin{itemize}
  \item[\checkbox] Insulation improvements
  \item[\checkbox] Window upgrades
  \item[\checkbox] Air leak fixes
  \item[\checkbox] Heating, ventilation, and air conditioning (HVAC) improvements
  \item[\checkbox] Energy efficient appliance installations
  \item[\checkbox] \textit{Exterior upgrades (roofing, siding, etc.}
  \item[\checkbox] \textit{Aesthetic updates}
  \item[\checkbox] \textit{Home addition}
  \item[\checkbox] \textit{Major renovation}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Are you aware of the type of construction material your home consists of?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they select yes in the previous example):}
What is the primary construction material of your home?
\begin{itemize}
  \item[\checkbox] Brick
  \item[\checkbox] Concrete
  \item[\checkbox] Steel
  \item[\checkbox] Wood
  \item[\checkbox] \textit{Stone}
  \item[\checkbox] Other: please specify
\end{itemize}
 

\item Besides small kitchen appliances, TVs, and computers, what major electric appliances are present in your home? Check all that apply.
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance heater, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Swamp cooler
  \item[\checkbox] Whole house fan
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other (key in)
\end{itemize}
 
\textit{These choices are carried forward to multiple proceeding questions.}
 

\item To show that you are paying attention, please select ``All of the above''.
 

\item Besides smart TVs, smart phones or other smart personal devices, do you have any smart appliances in your home (e.g.\ internet connected and allow for remote control, monitoring, and automation)?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they answered yes to having a smart device in the home):}
Which smart devices do you own?
\begin{itemize}
  \item[\checkbox] Smart thermostat
  \item[\checkbox] Home energy management system (HEMS)
  \item[\checkbox] Smart EV charger
  \item[\checkbox] Dishwasher
  \item[\checkbox] Refrigerator
  \item[\checkbox] Washer and/or Dryer
  \item[\checkbox] \textit{Microwave}
  \item[\checkbox] \textit{Water heater}
  \item[\checkbox] \textit{Lighting}
  \item[\checkbox] \textit{Vacuum cleaner}
  \item[\checkbox] \textit{Stove}
  \item[\checkbox] \textit{Medical device(s)}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested question based on the one above (They will only see options for the ones they chose above):}
On average, what electric appliances do you generally use between 1 and 7 pm on an average \textbf{winter weekday} (Monday through Friday)? (check all that apply)
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other major appliances (please specify)
\end{itemize}
 

\item \textit{Nested question based on the one above (They will only see options for the ones they chose above):}
On average, what electric appliances do you generally use between 1 and 7 pm on an average \textbf{summer weekday} (Monday through Friday)? (check all that apply)
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested question based on the one above (They will only see options for the ones they chose above):}
On average, what electric appliances do you generally use between 1 and 7 pm on the \textbf{winter weekends and holidays}? (check all that apply)
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other major appliances (please specify)
\end{itemize}
 

\item \textit{Nested question based on the one above (They will only see options for the ones they chose above):}
On average, what electric appliances do you generally use between 1 and 7 pm on the \textbf{summer weekends and holidays}? (check all that apply)
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other major appliances (please specify)
\end{itemize}
 

\item Does the electricity rate have an impact on your decision on when you use certain appliances? Specifically, if the price of electricity at a certain time of day, week, or year is lower or higher may affect when you use an appliance.
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] Sometimes
  \item[\checkbox] My electricity price does not change
\end{itemize}
 

\item \textit{Nested question based on their answer above and which appliances are present:}
Of the appliances present in your home, which ones do you change your usage of because of your electricity rate? Check all that apply.
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, patient lift, etc.)
  \item[\checkbox] None
  \item[\checkbox] Other major appliances (please specify)
\end{itemize}
 

\item \textit{Nested question based on their answer above:}
Generally, which \textbf{days of the week} are you more willing to change your electricity usage habits (e.g., shift or decrease your electricity usage to other days of the week)? Check all that apply.
\begin{itemize}
  \item[\checkbox] Weekdays
  \item[\checkbox] Weekends
\end{itemize}
 

\item \textit{Nested question based on their answer above:}
Which \textbf{times of the day} are you more willing to change your electricity habits? (e.g.\ Shift or decrease your electricity usage to other times of the day)? Check all that apply.
\begin{itemize}
  \item[\checkbox] 5 am -- 8 am
  \item[\checkbox] 8 am -- 1 pm
  \item[\checkbox] 1 pm -- 7 pm
  \item[\checkbox] 7 pm -- 9 pm
  \item[\checkbox] 9 pm -- 5 am
\end{itemize}
 

\item Suppose that your electric utility introduces a program where they can automatically make changes to your heating and/or cooling system, for instance its operation or the set-points, in order to reduce your electricity bill. Would you be willing to enroll in such a program?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they answer yes to the question above):}
What percentage savings on your electricity bill would make you willing to participate in such a program?
\begin{itemize}
  \item[\checkbox] At least 10\% off my electricity bill
  \item[\checkbox] At least 20\% off my electricity bill
  \item[\checkbox] At least 30\% off my electricity bill
  \item[\checkbox] At least 40\% off my electricity bill
  \item[\checkbox] 50\% or more off my electricity bill
\end{itemize}
 

\item \textit{Nested from above (If they answered no to both questions):}
Is there any amount of savings that would make you change your mind (i.e.\ convince you to be willing to participate in a program as described)?
\begin{itemize}
  \item[\checkbox] At least 10\% off my electricity bill
  \item[\checkbox] At least 20\% off my electricity bill
  \item[\checkbox] At least 30\% off my electricity bill
  \item[\checkbox] At least 40\% off my electricity bill
  \item[\checkbox] 50\% or more off my electricity bill
  \item[\checkbox] No amount of savings could convince me to participate in such a program
\end{itemize}
 

\item Suppose you have an app or smart device that can determine a range of temperatures based on your comfort preferences and the utility cannot go outside this range. Would this change your mind in participating in this program?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they answered no to being willing to participate):}
What are your main concerns about participating in such a program? (check all that apply)
\begin{itemize}
  \item[\checkbox] Privacy concerns
  \item[\checkbox] I do not want to give the utility permission to control anything in my home
  \item[\checkbox] I am concerned that it might damage my heating and/or cooling system
  \item[\checkbox] I do not want to sacrifice my comfort
  \item[\checkbox] These financial incentives are not significant to me
  \item[\checkbox] \textit{Medical concerns}
  \item[\checkbox] \textit{Ineligible to participate}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested question based on the appliances identified (If they have an electric heater):}
Is your heating thermostat automatic or manual?
\begin{itemize}
  \item[\checkbox] Programmable
  \item[\checkbox] Manual
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested question based on whether they have an electric heater or not:}
What is your heater generally set to in the winter when you are home?
\begin{itemize}
  \item[\checkbox] Below 60
  \item[\checkbox] 60--65
  \item[\checkbox] 65--68
  \item[\checkbox] 68--70
  \item[\checkbox] Above 70
  \item[\checkbox] I do not generally run my heater
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested question based on whether they have an electric heater or not:}
Do you generally adjust the heating temperature when you leave for work?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] It automatically adjusts
\end{itemize}
 

\item \textit{Nested question based on whether they have an electric heater or not:}
Do you generally adjust the heater setpoint during nighttime?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] It automatically adjusts
\end{itemize}
 

\item \textit{Nested question based on whether they have a heater or not:}
When it is too cold, how do you adjust your thermostat setpoint?
\begin{itemize}
  \item[\checkbox] Not at all
  \item[\checkbox] Adjust it slightly towards more comfort (1--2 degrees)
  \item[\checkbox] Adjust it as much as necessary towards more comfort (more than 2 degrees)
  \item[\checkbox] Adjust it to save money
\end{itemize}
 

\item \textit{Nested question based on the appliances identified (If they have an electric A/C or swamp cooler):}
Is your cooling thermostat programmable (the temperature changes at various times of the day based on your preferences) or changed manually (you physically adjust the temperature when desired)?
\begin{itemize}
  \item[\checkbox] Programmable
  \item[\checkbox] Manual
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested question based on whether they have an A/C or not:}
What temperature is your A/C generally set to in the summer when you are home?
\begin{itemize}
  \item[\checkbox] Below 60
  \item[\checkbox] 60--65
  \item[\checkbox] 65--70
  \item[\checkbox] 70--75
  \item[\checkbox] 75--80
  \item[\checkbox] Above 80
  \item[\checkbox] I do not generally run my A/C
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested question based on whether they have an A/C or not:}
Do you generally adjust the A/C temperature when you leave for work?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] It automatically adjusts
\end{itemize}
 

\item \textit{Nested question based on whether they have an A/C or not:}
Do you generally adjust the A/C temperature during nighttime?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] It automatically adjusts
\end{itemize}
 

\item \textit{Nested question based on whether they have an A/C or not:}
When it is too hot, how do you adjust your thermostat setpoint?
\begin{itemize}
  \item[\checkbox] Not at all
  \item[\checkbox] Adjust it slightly towards more comfort (1--2 degrees)
  \item[\checkbox] Adjust it as much as necessary towards more comfort (more than 2 degrees)
  \item[\checkbox] Adjust it to save money
\end{itemize}
 

\item \textit{Nested question based on the answer above (If manual thermostat):}
Do you adjust the setpoints of your thermostat (heating and/or cooling) periodically? Check all that apply.
\begin{itemize}
  \item[\checkbox] Yes, I set the temperature based on when I am home
  \item[\checkbox] Yes, I set the thermostat based on the outdoor temperature
  \item[\checkbox] No, I set my thermostat and leave it for extended periods of time
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested question based on whether there are medical devices in the home:}
Which medical devices are present in your home (check all that apply):
\begin{itemize}
  \item[\checkbox] Hospital bed
  \item[\checkbox] Mobility device (stair lift, electric wheelchair, etc.)
  \item[\checkbox] Dialysis machine
  \item[\checkbox] Ventilator
  \item[\checkbox] Oxygen concentrator
  \item[\checkbox] Respirator
  \item[\checkbox] \textit{CPAP machine}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Would you be willing to participate in a program in which the electric utility pays you to reduce your electricity usage at various times of the year, for instance, when the weather is exceptionally hot or cold?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested from above (If they answer yes, they will see this question):}
What form of incentive would you prefer? (select all that apply):
\begin{itemize}
  \item[\checkbox] An annual payment from the utility if they reduce my electricity usage
  \item[\checkbox] Percentage reduction in your bill
  \item[\checkbox] Financial incentives are not a determining factor in my participation
  \item[\checkbox] \textit{Rebate or technology purchase credit}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested from above (If they answered annual payment):}
What amount of annual payment would make you willing to participate in a program as described?
\begin{itemize}
  \item[\checkbox] At least \$25
  \item[\checkbox] At least \$50
  \item[\checkbox] At least \$100
  \item[\checkbox] At least \$200
  \item[\checkbox] More than \$200
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested from above (If they answered percentage reduction in bill):}
What percentage savings on your electricity bill would make you willing to participate in a program as described?
\begin{itemize}
  \item[\checkbox] At least 10\%
  \item[\checkbox] At least 20\%
  \item[\checkbox] At least 30\%
  \item[\checkbox] At least 40\%
  \item[\checkbox] 50\% or more
  \item[\checkbox] I don't know
\end{itemize}
 

\item \textit{Nested from above (If they said they wouldn't participate):}
What are your main concerns about participating in such a program? (check all that apply)
\begin{itemize}
  \item[\checkbox] Privacy concerns
  \item[\checkbox] I do not want to sacrifice my comfort
  \item[\checkbox] These financial incentives are not significant to me
  \item[\checkbox] \textit{Ineligibility}
  \item[\checkbox] \textit{This is out of my control}
  \item[\checkbox] \textit{Lack of trust in the utility}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Do you have any pets or livestock? (check all that apply).
\begin{itemize}
  \item[\checkbox] None
  \item[\checkbox] Bird(s)
  \item[\checkbox] Cat(s)
  \item[\checkbox] Dog(s)
  \item[\checkbox] Fish
  \item[\checkbox] Livestock
  \item[\checkbox] Reptile(s)
  \item[\checkbox] None
\end{itemize}
 

\item \textit{Nested question based on whether they have a pet or not:}
Does this pet/pets require any specialized electric appliance?
\begin{itemize}
  \item[\checkbox] No
  \item[\checkbox] Water filter
  \item[\checkbox] Heat lamp or other electric space heater
  \item[\checkbox] Fans or other electric space cooler
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Do you own an electric vehicle (EV)?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested question based on whether there is/are EV(s) present in the home:}
When do you generally charge your EV at home? (check all that apply):
\begin{itemize}
  \item[\checkbox] Every day
  \item[\checkbox] A few times a week but only during the week
  \item[\checkbox] A few times a week upon need
  \item[\checkbox] Only during weekends
  \item[\checkbox] I do not charge at home
\end{itemize}
 

\item \textit{Nested question based on whether they charge on a weekday:}
What time of day do you generally charge your EV on a \textbf{weekday}? (check all that apply):
\begin{itemize}
  \item[\checkbox] Morning
  \item[\checkbox] Midday
  \item[\checkbox] Evening
  \item[\checkbox] Overnight
\end{itemize}
 

\item \textit{Nested question based on whether they charge on a weekend:}
What time of day do you generally charge your EV on the \textbf{weekend}? (check all that apply):
\begin{itemize}
  \item[\checkbox] Morning
  \item[\checkbox] Midday
  \item[\checkbox] Evening
  \item[\checkbox] Overnight
\end{itemize}
 

\item When deciding to charge your EV, does the price of electricity have an impact on when you do so?
\begin{itemize}
  \item[\checkbox] Yes
  \item[\checkbox] No
  \item[\checkbox] Sometimes
\end{itemize}
 

\item \textit{Nested question based on which appliances they identified in their home:}
Of the electric appliances, medical devices (if applicable), and EVs (if applicable) are you \textbf{least} likely to use at a different time of day or day of the week if requested by the utility?
\begin{itemize}
  \item[\checkbox] Heating (heat pump, resistance, etc.)
  \item[\checkbox] Air conditioning (A/C)
  \item[\checkbox] Dishwasher
  \item[\checkbox] Clothes washer and/or dryer
  \item[\checkbox] Electric stove and/or oven
  \item[\checkbox] Vacuum cleaner
  \item[\checkbox] Specialized medical equipment (mobility devices, hospital bed, etc.)
  \item[\checkbox] Electric vehicle (EV)
  \item[\checkbox] Medical devices
  \item[\checkbox] Electric vehicle (EV)
  \item[\checkbox] None
  \item[\checkbox] \textit{I want to use my appliances when I see fit}
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item Do you have on-site generation or energy storage? (Select all that apply)
\begin{itemize}
  \item[\checkbox] Yes, battery
  \item[\checkbox] Yes, solar panel(s)
  \item[\checkbox] Yes, diesel generator
  \item[\checkbox] \textit{Propane generation}
  \item[\checkbox] \textit{Gasoline generation}
  \item[\checkbox] Other (key in)
  \item[\checkbox] No
\end{itemize}
 

\item \textit{Nested question based on whether they have on-site generation or storage:}
What was your main incentive(s) for installing this onsite generation in your home? (Check all that apply)
\begin{itemize}
  \item[\checkbox] Cost savings
  \item[\checkbox] Reliability
  \item[\checkbox] Reduced carbon footprint
  \item[\checkbox] Increased home value
  \item[\checkbox] Grid independence
  \item[\checkbox] Other (key in)
\end{itemize}
 

\item \textit{Nested question based on whether they chose on-site generation or storage because of cost savings:}
What percentage decrease of your electricity bill do you think this onsite generation resource provides?
\begin{itemize}
  \item[\checkbox] Less than 10\%
  \item[\checkbox] 10--20\%
  \item[\checkbox] 20--30\%
  \item[\checkbox] 30--40\%
  \item[\checkbox] 40--50\%
  \item[\checkbox] More than 50\%
\end{itemize}
 

\item During the week (Monday through Friday), when are you generally present in your home? (check all that apply)
\begin{itemize}
  \item[\checkbox] 5 am -- 8 am
  \item[\checkbox] 8 am -- 1 pm
  \item[\checkbox] 1 pm -- 7 pm
  \item[\checkbox] 7 pm -- 9 pm
  \item[\checkbox] 9 pm -- 5 am
\end{itemize}
 

\item On the weekend (Saturday and Sunday), when are you generally present in your home? (check all that apply)
\begin{itemize}
  \item[\checkbox] 5 am -- 8 am
  \item[\checkbox] 8 am -- 1 pm
  \item[\checkbox] 1 pm -- 7 pm
  \item[\checkbox] 7 pm -- 9 pm
  \item[\checkbox] 9 pm -- 5 am
\end{itemize}
 

\item You have completed all questions in the survey. If applicable, please provide any comments or concerns that were not already covered previously. If there is anything else you would like to add, this is the space to do so. Thank you.\\
\textit{Free response}
\end{enumerate}

\end{document}
